Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-10 exp1/iswc2013.tex
invalidated due to absence of solution modifiers
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@557 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{frac64normal.pdf}
  \caption{A normal plot of the Fractional Factorial Experiment with
    64 runs. The labelled points are considered significant by using
    the Lenth criterion. Triangles correspond to a level $\alpha=0.15$
    and crosses at $\alpha=0.05$.}\label{fig:frac64normal}
\end{figure}

@@

>>>>

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{frac64normal.pdf}
  \caption{A normal plot of the Fractional Factorial Experiment with
    64 runs. The labelled points are considered significant by using
    the Lenth criterion. Triangles correspond to a level $\alpha=0.15$
    and crosses at $\alpha=0.05$. The use of different symbols have
    been added to FrF2 by the authors.}\label{fig:frac64normal}
\end{figure}

@@

Finally, we note that the most problematic cases are those that are
covered neither by the broad factors, nor the lurking variables, or
any of the specific factors. We cannot in the general case be sure
that they are accounted for, so reviewers must remain vigilant that
some factors are simply ignored. What finally invalidates the present
experiment is the complete absence of certain obvious language
features, such as solution modifiers.
